Viscous Erosion in Porous Media

### 2018-03-28 docs/methods/erosion_methods.tex
NM

These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state. In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners. In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma$ taking the values 20/1024, 10/1024, and 5/1024) to assess how the numerical regularization influences shape. Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time. The initially circular geometry has an aspect ratio of unity, and, as erosion carves a more slender form, the aspect ratio increases monotonically. The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$. In the simulation with these least smoothing ($\eps = \sigma = 5/1024$), the aspect ratio tends to a value of 2.7 in long time.

Next, we aim to measure the opening angle of the front/rear corner. Since these simulated bodies are actually smooth, though, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points. To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5). We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there. Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements. In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters. The method gives an angle measurement of $180^{\circ}$ for the initially circular geometry, thus providing some confirmation. As time moves forward, erosion carves a sharper corner and the angle decreases monotonically. Here, the effect of the smoothing parameters is more visible, but we still see convergence as $\eps, \sigma \to 0$. In the most accurate simulation (black), the opening angle converges to a value of $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.

>>>>

These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state. In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners. In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters (keeping $\eps = \sigma$ and taking the values 20/1024, 10/1024, and 5/1024) to assess how the numerical regularization influences shape. Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time. The initially circular geometry has an aspect ratio of unity, and, as erosion carves a more slender form, the aspect ratio increases monotonically. The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$. In the simulation with these least smoothing ($\eps = \sigma = 5/1024$), the aspect ratio tends to a value of 2.7 in long time.

Next, we aim to measure the opening angle of the front/rear corner. Since these simulated bodies are actually smooth, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points. To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5). We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there. Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements. In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters. 
The method gives an angle measurement of $180^{\circ}$ for the initially circular geometry, thus providing some confirmation. As time moves forward, erosion carves a sharper corner and the angle decreases monotonically. Here, the effect of the smoothing parameters is more visible, but we still see convergence as $\eps, \sigma \to 0$. In the most accurate simulation (black), the opening angle converges to a value of $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.
